\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-06-15 forwards-and-backwards.tex
Update on Overleaf.

\paragraph{Remark:}
An equivalent way to describe the model would be to say that
when the state of the population is $\eta$,
an individual at $x$ gives birth at rate
$$
    \theta \gamma(x, \smooth{\gamma} \eta(x))
    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x, dy)
    :=
    \frac{
        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{N \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta^{\theta}(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

\begin{corollary}[Deterministic limits]
    \label{cor:nonlocal_pde_limits}
    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
    if the limit is deterministic (i.e., $\theta / N \to \alpha = 0$),
    then any limit $\eta_t$ is a weak solution to the nonlocal partial differential equation
    \begin{equation} \label{eqn:nonlocal_pde}
        \partial_t \varphi_t(x)
        =
        r\left(x, \smooth{r} \varphi_t(x) \right)
        \DG^* \left[
            \varphi_t(\cdot)
            \gamma\big( x, \smooth{\gamma} \varphi_t(\cdot) \big)
        \right](x)
        +
        \varphi_t(x)
        F\left(x, \smooth{F} \varphi_t(x) \right)
        ,
    \end{equation}
    in the sense of Definition~\ref{defn:weak_solutions}.
    If equation \eqref{eqn:nonlocal_pde} has a unique solution,
    then $(\eta^N_t)_{t \ge 0}$ converges to that solution.
\end{corollary}

@@

Concretely, then: for each label $a$ in
$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$
let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
The mean measure is a product of Lebesgue measure on the first two coordinates,
$q(0, \cdot)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
It will also be convenient
to suppose that for each label $a$ we have an enumeration of the points in $\Pi_a$,
so we may refer to ``the $j^\text{th}$ point in $\Pi_a$'',
although the precise order of this enumeration is irrelevant.
If $(t, v, y, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
then $t$ will determine possible birth times,
$v$ will determine levels of the offspring,
$y$ will give the spatial displacement of the offspring relative to the parent,
$\kappa$ will be used to determine whether parent or offspring are assigned the new level,
and the new label produced will be $a \concat j$,
i.e., the label $a$ with $j$ appended (so, if $a \in \IN_{\ge 0}^k$ then $a \concat j \in \IN_{\ge 0}^{k+1}$).
Each label $a$ has a birth time $\tau_a$,
when it is first assigned,
and a death time $\sigma_a$, when its level first hits $N$.
For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
of the individual carrying label $a$ at time $t$.
Now, since we have defined labels so that the level does not jump,
$U_a$ satisfies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
\begin{equation} \label{eqn:U_line_of_descent}
    \begin{split}
& U_a(t)
    =
    U_a(\tau_a) \\
&\qquad {}   
    + \int_{\tau_a}^{t}
    \left(
        \frac{\theta}{N} \gamma(X_a(s),\eta_s)
        \int_{\IR^d} r(z,\eta_s) q(X_a(s),dz) U_a(s)^2
        -
        b(X_a(s),\eta_s) U_a(s)
    \right)
    ds ,
\end{split}
\end{equation}
and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > N\}$.

Potential reproduction events occur at times $\tau_a + s$
for each point $(s, v, y, \kappa) \in \Pi_a$.
We say `potential' since if the resulting level is greater than $N$,
the event does not happen.
If this is the $j^\text{th}$ point in $\Pi_a$,
the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau_a + s$.
For convenience define
$$
    \ell(x, y, \eta, v)
    =
    \frac{
        v
    }{
        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
    } ,
$$
and using this, the (potential) new level is
\begin{equation*}
    U_{a \concat j}(\tau_{a \concat j})
    =
    U_a(\tau_{a \concat j})
    +
    \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-), v) .
\end{equation*}
If $U_{a \concat j}(\tau_{a \concat j}) < N$,
the new individual labeled $a \concat j$ is produced,
\plr{TODO: explain why this does the right thing}
and $\kappa$ determines which label is associated with the new location,
so
\begin{align*}
    X_{a \concat j}(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + (1 - \kappa) y .
\end{align*}
On the other hand
if $U_{a \concat j}(\tau_{a \concat j}) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
so
\begin{align} \label{eqn:X_line_of_descent}
    X_a(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < N} .
\end{align}
Recall that the parental \emph{individual} always retains their spatial location,
so that $\kappa = 0$ corresponds to the parent being assigned a new level,
and our line of descent switching to the offspring.

@@

Under this notation, for $t>\tau_{[a]_k}$,

\begin{equation}
\label{eq: space_across_lineage}
\begin{aligned}
&X^{N}_{[a]_{k}}(t)- X^{N}_{[a]_{0}}(0)\\
=& \sum_{i=1}^{k}
\sum_{j=1}^{a_i-1}
(1-\kappa_{[a]_{i-1}\concat j}) y_{[a]_{i-1}\concat j} \ind_{U_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}\\
&+ \sum_{i=1}^{k}
\kappa_{[a]_i} y_{[a]_i} \ind_{U_{[a]_i}(\tau_{[a]_i}) < N}\\
&+\int_{\tau_{[a]_k}}^{t}
(1-\kappa)y
\ind_{ \{
        U_{[a]_k}(\tau_{[a]_k}+s)
        +\ell(X_{[a]_k}(\tau_{[a]_k}+s),y,\eta_{[a]_k}(\tau_{[a]_k}+s),v) < N
        \}
      } 
\Pi_{[a]_k}(dsdvdyd\kappa),
\end{aligned}    
\end{equation}
where the first term
corresponds to 
the sum of $a_{i}-1$ many potential jumps
in the $(i-1)-th$ generation;
the second term corresponds to 
the sum of $k$ many potential jumps
when the $k$-th generation is introduced;
and the last term
corresponds to sum of 
potential jumps that occured in
the current generation from 
time $\tau_{[a]_k}$
to current time $t >\tau_{[a]_k}$.

@@

\begin{proposition}[Line of descent construction]
Let $\beta(x, \eta) = \meanq + 2 \covq \grad \log r(x, \eta)$
and $K$ such that $\covq = K K^T$.
Associate with each label $a \in \labelspace$
an independent $d$-dimensional Brownian motion $W_a$
and an independent Poisson process $R_a$ on $[0, \infty)^2$
with Lebesgue mean measure,
as before with points ordered in some way.
Given $\eta_0 \in \measures$,
let $(x_i, u_i)$ be the points of a Poisson process
with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta_0$ and Lebesgue measure.
For each point begin a line of descent
with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
Suppose that the spatial locations and level of each line of descent $a$
behave, for $\tau_a \le t < \sigma_a$ as, as
\begin{align*}
X_a(t)
    &=
    X_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \beta(x, \eta(s)) ds
        +
        K dW_a(s)
    \bigg)
    ds  \\
U_a(t)
    &=
    U_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \alpha \gamma(X_a(s),\eta(s))
        r(x,\eta(s)) U_a(s)^2
\\ &\qquad \qquad \qquad {}   
        -
        \left\{
            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
            + F(X_a(s), \eta(s))
        \right\}
        U_a(s)
    \bigg)
    ds .
\end{align*}
Each point in the $R_a$ denotes a potential birth time for $a$:
if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $t < \sigma_a - \tau_a$,
then a new line of descent with label $a \concat j$ is produced,
with birth time $\tau_{a \concat j} = \tau_a + t$,
location $X_{a \concat j}(\tau_a + t) = X_a(tau_a + t)$, and level
$$
    U_{a \concat j}(\tau_a + t) = U_a(\tau_a + t)
    + \frac{v}{ 2 \alpha \gamma(X_a(\tau_a + t), \eta_{\tau_a + t}) r(X_a(\tau_a + t), \eta_{\tau_a + t}) } .
$$
For each $a$, let $\sigma_a = \inf\{t \ge 0: U_a(t) < \infty\}$.
Then, the processes defined by
\begin{align*}
    \eta_t = \lim_{N \to \infty} \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
    \qquad \text{and} \qquad
    \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
\end{align*}
agree in distribution with those of Definitions~\ref{defn:mgale_construction} and~\ref{defn:lookdown_mgale},
respectively.
\end{proposition}

@@

\begin{lemma}[Compact Containment for the population process]
    \label{lem: Compact Containment}
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
uniformly in $\theta$.
In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
\begin{equation}
\limsup_{N \to \infty}
    \mathbb{P}\left[\sup_{s \in [0,T]}
        \langle 1 ,\eta^{\theta}_{s}\rangle
        > K_\epsilon \right]
        \leq \frac{C(T)}{K_{\epsilon}} < \epsilon.    
\end{equation}
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
        -\langle 1,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

@@

% % % % % % % % % % % % %
\subsection{Tightness of the lookdown process}
    \label{sec:lookdown_tightness_proofs}

@@

In Appendix \ref{sec: Topologies on Lookdown},
we will prove that
tightness of the whole lookdown process
holds given
tightness of 
all ancestral lineages
in a countable product topology.

@@

\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,\theta, \lambda}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},

@@

\subsection{Weak-Vague Topology on Measures}\label{sec: Empirical Measure Topology}

@@

\begin{definition}
We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\mathbb{R}^d \times [0, \infty) \to \mathbb{R})$ such that 
$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $C_g>0$, such that $g(x,u)=1$ for all $u \geq C_g$.
\end{definition}

@@

\bibliographystyle{plainnat}
\bibliography{refs.bib,plr_refs.bib}

>>>>

\paragraph{Remark:}
An equivalent way to describe the model would be to say that
when the state of the population is $\eta$,
an individual at $x$ gives birth at rate
$$
    \theta \gamma(x, \smooth{\gamma} \eta(x))
    \int r(x, \smooth{r} \eta(y)) q(x, dy) ,
$$
and that offspring disperse according to the kernel
$$
    q_\theta^\mathfrak{m}(x,\eta,  dy)
    :=
    \frac{
        r(y, \smooth{r} \eta(y)) q_\theta(x, dy)
    }{
        \int r(x, \smooth{r} \eta(z)) q_\theta(x, dz)
    } .
$$
Clearly, the random walk driven by this dispersal kernel
should be biased towards regions of higher establishment probability.
For comparison to future results,
it is interesting to write down the limiting generator:
\begin{align*}
    \lim_{N \to \infty}
    \theta \int (f(y) - f(x)) q_\theta^\mathfrak{m}(x, \eta, dy)
    &=
    \frac{
        \DG\left[ f(\cdot) r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
        - 
        f(\cdot) \DG\left[ r(\cdot, \smooth{r} \eta(\cdot)) \right](x)
    }{
        r(x, \smooth{r} \eta^{\theta}(x))
    } .
\end{align*}
In the simplest case of unbiased, isotropic dispersal,
$\meanq = 0$ and $\covq = I$, so $\DG = \Delta$,
and this is equal to
\begin{align*}
    \Delta f(x) + 2 \grad f(x) \cdot \grad \log r(\cdot, \smooth{r} \eta(\cdot))(x) .
\end{align*}
However, we will see that following a lineage back through the population
has a different behavior yet again.

@@

\begin{corollary}[Deterministic limits]
    \label{cor:nonlocal_pde_limits}
    Under the assumptions of Theorem~\ref{thm:nonlocal_convergence},
    if the limit is deterministic (i.e., $N^{-1}\theta \to \alpha = 0$),
    then any limit $\eta_t$ is a weak solution to the nonlocal partial differential equation
    \begin{equation} \label{eqn:nonlocal_pde}
        \partial_t \varphi_t(x)
        =
        r\left(x, \smooth{r} \varphi_t(x) \right)
        \DG^* \left[
            \varphi_t(\cdot)
            \gamma\big( x, \smooth{\gamma} \varphi_t(\cdot) \big)
        \right](x)
        +
        \varphi_t(x)
        F\left(x, \smooth{F} \varphi_t(x) \right)
        ,
    \end{equation}
    in the sense of Definition~\ref{defn:weak_solutions}.
    If equation \eqref{eqn:nonlocal_pde} has a unique solution,
    then $(\eta^N_t)_{t \ge 0}$ converges to that solution.
\end{corollary}

@@

Concretely, then: for each label $a$ in
$\labelspace = \bigcup_{k \ge 1} \IN_{\ge 1}^k$
let $\Pi_a$ be an independent Poisson process on $[0, \infty)^2 \times \IR_d \times \{0,1\}$.
The mean measure is a product of Lebesgue measure on the first two coordinates,
the density of the standard Gaussian $N(0,1)$ on $\IR^d$, and $(\delta_0 + \delta_1)/2$ on $\{0, 1\}$.
It will also be convenient
to suppose that for each label $a$ we have an enumeration of the points in $\Pi_a$,
so we may refer to ``the $j^\text{th}$ point in $\Pi_a$'',
although the precise order of this enumeration is irrelevant.
If $(t, v, z, \kappa)$ is the $j^\text{th}$ point in $\Pi_a$,
then $t$ will determine possible birth times,
$v$ will determine levels of the offspring,
$z$ will give the spatial displacement of the offspring relative to the parent,
$\kappa$ will be used to determine whether parent or offspring are assigned the new level,
and the new label produced will be $a \concat j$,
i.e., the label $a$ with $j$ appended (so, if $a \in \IN_{\ge 0}^k$ then $a \concat j \in \IN_{\ge 0}^{k+1}$).
Each label $a$ has a birth time $\tau_a$,
when it is first assigned,
and a death time $\sigma_a$, when its level first hits $N$.
For any $\tau_a \le t \le \sigma_a$ we denote by $X_a(t)$ and $U_a(t)$ the spatial location and level
of the individual carrying label $a$ at time $t$.
Now, since we have defined labels so that the level does not jump,
$U_a$ satisfies~\eqref{eqn:dot_u} for $\tau_a \le t \le \sigma_a$, i.e.,
\begin{equation} \label{eqn:U_line_of_descent}
    \begin{split}
& U_a(t)
    =
    U_a(\tau_a) \\
&\qquad {}   
    + \int_{\tau_a}^{t}
    \left(
        \frac{\theta}{N} \gamma(X_a(s),\eta_s)
        \int_{\IR^d} r(z,\eta_s) q(X_a(s),dz) U_a(s)^2
        -
        b(X_a(s),\eta_s) U_a(s)
    \right)
    ds ,
\end{split}
\end{equation}
and, of course, $\sigma_a = \inf\{t \ge \tau_a : U_a(t) > N\}$.

Potential reproduction events occur at times $\tau_a + s$
for each point $(s, v, w, \kappa) \in \Pi_a$.
We say `potential' since if the resulting level is greater than $N$,
the event does not happen.
If this is the $j^\text{th}$ point in $\Pi_a$,
the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau_a + s$.
Similarly, the potential birth location is 
$$y(z) = \frac{1}{\theta}\meanq(X_a(\tau_{a+j}-)) + \frac{1}{\sqrt{\theta}}K(X_a(\tau_{a+j}-))z,$$
where $K(x)K^{T}(x)=\covq(x)$.

For convenience define
$$
    \ell(x, y, \eta, v)
    =
    \frac{
        v
    }{
        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
    } ,
$$
and using this, the (potential) new level is
\begin{equation*}
    U_{a \concat j}(\tau_{a \concat j})
    =
    U_a(\tau_{a \concat j})
    +
    \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-), v) .
\end{equation*}
If $U_{a \concat j}(\tau_{a \concat j}) < N$,
the new individual labeled $a \concat j$ is produced,
\plr{TODO: explain why this does the right thing}
and $\kappa$ determines which label is associated with the new location,
so
\begin{align*}
    X_{a \concat j}(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + (1 - \kappa) y .
\end{align*}
On the other hand
if $U_{a \concat j}(\tau_{a \concat j}) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
so
\begin{align} \label{eqn:X_line_of_descent}
    X_a(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < N} .
\end{align}
Recall that the parental \emph{individual} always retains their spatial location,
so that $\kappa = 0$ corresponds to the parent being assigned a new level,
and our line of descent switching to the offspring.

@@

Finally, we write $S(\tau_{[a]_k},t):=[\tau_{[a]_k},t]\times[0,\infty)\times\mathbb{R}^d \times \{0,1\}$.
Under this notation, for $t>\tau_{[a]_k}$,

\begin{equation}
\label{eq: space_across_lineage}
\begin{aligned}
&X^{N}_{[a]_{k}}(t)- X^{N}_{[a]_{0}}(0)\\
=& \sum_{i=1}^{k}
\sum_{j=1}^{a_i-1}
(1-\kappa_{[a]_{i-1}\concat j}) y_{[a]_{i-1}\concat j} \ind_{U_{[a]_{i-1}\concat j}(\tau_{[a]_{i-1}\concat j}) < N}\\
&+ \sum_{i=1}^{k}
\kappa_{[a]_i} y_{[a]_i} \ind_{U_{[a]_i}(\tau_{[a]_i}) < N}\\
&+\int_{S(\tau_{[a]_k},t)}
(1-\kappa)y(z)
\ind_{ \{
        U_{[a]_k}(\tau_{[a]_k}+s)
        +\ell(X_{[a]_k}(\tau_{[a]_k}+s),y,\eta_{[a]_k}(\tau_{[a]_k}+s),v) < N
        \}
      } 
\Pi_{[a]_k}(dsdvdzd\kappa),
\end{aligned}    
\end{equation}
where the first term
corresponds to 
the sum of $a_{i}-1$ many potential jumps
in the $(i-1)-th$ generation;
the second term corresponds to 
the sum of $k$ many potential jumps
when the $k$-th generation is introduced;
and the last term
corresponds to sum of 
potential jumps that occured in
the current generation from 
time $\tau_{[a]_k}$
to current time $t >\tau_{[a]_k}$.

@@

\begin{proposition}[Line of descent construction]
Let $\beta(x, \eta) = \meanq + 2 \covq \grad \log r(x, \eta)$
and $K$ such that $\covq = K K^T$.
Associate with each label $a \in \labelspace$
an independent $d$-dimensional Brownian motion $W_a$
and an independent Poisson process $R_a$ on $[0, \infty)^2$
with Lebesgue mean measure,
as before with points ordered in some way.
Given $\eta_0 \in \measures$,
let $(x_i, u_i)$ be the points of a Poisson process
with mean measure on $\IR^d \times [0, \infty)$ a product of $\eta_0$ and Lebesgue measure.
For each point begin a line of descent
with label $i$, location $X_i(0) = x_i$, level $U_a(0) = u_i$, and birth time $\tau_i = 0$.
Suppose that the spatial locations and level of each line of descent $a$
behave, for $\tau_a \le t < \sigma_a$ as, as
\begin{align*}
X_a(t)
    &=
    X_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \beta(x, \eta(s)) ds
        +
        K dW_a(s)
    \bigg)
    ds  \\
U_a(t)
    &=
    U_a(\tau_a)
    + \int_{\tau_a}^{t}
    \bigg(
        \alpha \gamma(X_a(s),\eta(s))
        r(x,\eta(s)) U_a(s)^2
\\ &\qquad \qquad \qquad {}   
        -
        \left\{
            \gamma(X_a(s),\eta(s)) \DG r(X_a(s),\eta(s))
            + F(X_a(s), \eta(s))
        \right\}
        U_a(s)
    \bigg)
    ds .
\end{align*}
Each point in the $R_a$ denotes a potential birth time for $a$:
if the $j^\text{th}$ point in $R_a$ is $(t, v)$, with $t < \sigma_a - \tau_a$,
then a new line of descent with label $a \concat j$ is produced,
with birth time $\tau_{a \concat j} = \tau_a + t$,
location $X_{a \concat j}(\tau_a + t) = X_a(\tau_a + t)$, and level
$$
    U_{a \concat j}(\tau_a + t) = U_a(\tau_a + t)
    + \frac{v}{ 2 \alpha \gamma(X_a(\tau_a + t), \eta_{\tau_a + t}) r(X_a(\tau_a + t), \eta_{\tau_a + t}) } .
$$
For each $a$, let $\sigma_a = \inf\{t \ge 0: U_a(t) < \infty\}$.
Then, the processes defined by
\begin{align*}
    \eta_t = \lim_{N \to \infty} \frac{1}{N} \sum_{a : \tau_a \le t < \sigma_a} \delta_{X_a(t)}
    \qquad \text{and} \qquad
    \lp_t = \sum_{a : \tau_a \le t < \sigma_a} \delta_{(X_a(t), U_a(t))} 
\end{align*}
agree in distribution with those of Definitions~\ref{defn:mgale_construction} and~\ref{defn:lookdown_mgale},
respectively.
\end{proposition}

@@

\begin{lemma}[Compact Containment for the population process]
    \label{lem: Compact Containment}
Assume that $\eta^{\theta}_0 \to \eta_0$ weakly,
then for all $T>0$, there exists some constant $C(T)$,
such that
    \begin{align}
        \label{eq: Growth function bound on running sup}
        \IE\left[
            \sup_{0 \le t \le T}
            \langle 1, \eta^\theta_t \rangle
        \right]
        \le C(T) ,
    \end{align}
uniformly in $\theta$.
In particular, for any $\epsilon > 0$, there exists some $K_{\epsilon}>0$ such that
\begin{equation}
\limsup_{N \to \infty}
    \mathbb{P}\left[\sup_{s \in [0,T]}
        \langle 1 ,\eta^{\theta}_{s}\rangle
        > K_\epsilon \right]
        \leq \frac{C(T)}{K_{\epsilon}} < \epsilon.    
\end{equation}
\end{lemma}
\begin{proof}
We first take $f \equiv 1$ in Equation \eqref{eq: Pre-limit Martingale Characterisation}. We have that 
\begin{equation}
    \label{eq: Total Mass Martingale Characterisation}
\begin{aligned}
     M^{\theta}_t(1):=&  \langle 1,\eta^{\theta}_t \rangle
        -\langle 1,\eta^{\theta}_0 \rangle\\
 &-  \int_{0}^{t}\bigg\{   \int\left(   \int \theta
 \left(
        r\big(z,\rho_{r}*\eta^{\theta}_{s}(z)\big)
            -r\big(x,\rho_{r}*\eta^{\theta}_{s}(x)\big)
            \right)
                    q_\theta(x,dz)\right)
                            \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
                            \eta^{\theta}_{s}(dx)\\
& \qquad +\int F\big(x,\rho_{F}*\eta^{\theta}_{s}(x)\big)
\eta^{\theta}_{s}(dx)\bigg\} ds
\end{aligned}    
\end{equation}
is a martingale.
Therefore, taking expectations, we have
\begin{equation}\label{eq: Total mass control generalised}
\begin{aligned}
&\mathbb{E}[\langle 1 ,\eta^{\theta}_{t}\rangle] \\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] \\
&+ \int_{0}^{t}\mathbb{E}\bigg\langle
        \gamma\big(x,\rho_{\gamma}*\eta^{\theta}_{s}(x)\big)
            \left| \theta \int_{\mathbb{R}^n}
                    \big\{r\big(\rho_{r}*\eta^{\theta}_s(y)\big)-r\big(\rho_{r}*\eta^{\theta}_s(x)\big)\big\}
                    \rho_{1/\theta}(x-y)dy\right| + C_F 
                            ,\eta^{\theta}_s(dx)  \bigg\rangle ds\\
\leq &  \mathbb{E}[\langle 1 ,\eta^{\theta}_{0}\rangle] + (C_{\gamma,r} + C_F)\int_{0}^{t}\mathbb{E} \langle 1  ,\eta^{\theta}_s(dx) \rangle ds,
\end{aligned}
\end{equation}
where the last inequality holds by Lemma \ref{lem: gamma - r radius comparison}.

@@

% % % % % % % % % % % % %
\subsection{Tightness of the Lines of Descent}
    \label{sec:lookdown_tightness_proofs}

@@

@@

\mathbb{E}\left[e^{-\int_{S \times [0,\lambda]} f(x,u) \xi^{\epsilon,\theta,\lambda}(dx \times du)}\bigg| \mathcal{F}^{\Xi^{\epsilon,N}}_t\right]=e^{-\int F^{\epsilon,\theta,\lambda}_f(x) \Xi^{\epsilon,\theta,\lambda}_t(dx)},

@@

\subsection{Vague Topology on Measures}\label{sec: Empirical Measure Topology}

@@

\begin{theorem}
    \label{teo: Vague Relative Compactness through Projection}
For any Polish space $S$, let $f_1,f_2,...,$ be a dense collection of functions in $C^{+}_{K}$ that is closed under addition, then a set $A \in \mathcal{D}_{\mathcal{M}(S)}([0,\infty))$ is relative compact if and only if $Af_j = \{xf_j: x \in A\}$ is relatively compact on $\mathcal{D}_{[0, \infty)}([0,\infty))$ for every $j \in \mathbb{N}$.
\end{theorem}
\begin{proof}
See \cite{kallenberg1997foundations} Theorem A2.4.
\end{proof}
\begin{definition}
We define $\mathfrak{G}_{\leq 1}$ to be the set of functions $g \in \mathcal{C}(\mathbb{R}^d \times [0, \infty) \to \mathbb{R})$ such that 
$g(\cdot, u) \in \mathcal{C}_{0}(\mathbb{R}^d)$ for all $u \geq 0$, and there exists some $u_{*}>0$, such that $g(x,u)=1$ for all $u \geq u_{*}$.
\end{definition}

@@

Combining Theorem \ref{teo: Vague Relative Compactness through Projection} and Lemma \ref{lem: Dense set for test functions on empirical measures}, we have that $\{\xi^N_t: N \in \mathbb{N}\}$ is tight as a $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$-valued stochastic process in the vague topology as long as $\{F_g(\xi^N_t): N \in \mathbb{N}\}$ is tight as real-valued stochastic processes
for all $g \in \mathfrak{G}_{\leq 1}$. 
\bibliographystyle{plainnat}
\bibliography{refs.bib,plr_refs.bib}
